---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

![lifecycle](https://img.shields.io/badge/lifecycle-experimental-brightgreen.svg)

# flyingfox

The goal of `flyingfox` is to connect Quantopian's `zipline` financial backtesting package with R.

## Installation

You can install the released version of flyingfox from [CRAN](https://CRAN.R-project.org) with:

``` r
# NO YOU CANNOT
install.packages("flyingfox")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("DavisVaughan/flyingfox")
```

## Setup

(Using reticulate >= 1.7.1)

To get started with `zipline`, you'll need the `zipline` Python module. Install it with:

```{r, eval=FALSE}
install_zipline()
```

By default `zipline` will be installed into the virtualenv, `r-reticulate`, 
as recommended by `reticulate`.

Next, you'll need data to run the backtest on. The easiest way
to do this is to:

1) Create a free account on [Quandl](https://www.quandl.com/) and find your API Key in Account Settings. 2) Add the API key as the R environment variable, `QUANDL_API_KEY` (access your `.Renviron` variable with `usethis::edit_r_environ()`).
3) "Ingest" the Quandl data with `flyingfox::fly_ingest()`.

```{r, eval=FALSE}
fly_ingest()
```

## Example

`flyingfox` backtests are run using a combination of two main functions. `fly_initialize()` sets up variables you might need during the backtest along with giving you a chance to schedule functions to run periodically. `fly_handle_data()` is called at a daily/minutely frequency and runs your algorithm, orders assets, and records data for future inspection.

Below, we are going to create a basic mean reversion strategy to demonstrate the
basics of running an algorithm.

```{r}
library(flyingfox)
```

First, set up an initialize function. It must take `context` as the argument. 
Think of `context` as a persistent environment where you can store variables
and assets that you want to access at any point in the simulation.

```{r}
fly_initialize <- function(context) {

  # We want to track what day we are on. The mean reversion algo we use
  # should have at least 300 days of data before doing anything
  context$i = 0L

  # We want to trade apple stock
  context$asset = fly_symbol("AAPL")
}

```

Next, create a data handling function that accepts `context` and `data`. Think
of `data` as an environment containing functions for accessing historical and
current price data about the assets you are using in your simulation. 

The below implementation of `fly_handle_data()` demonstrates a mean reversion algorithm.

```{r}
fly_handle_data <- function(context, data) {

  # Increment day
  context$i <- context$i + 1L

  # While < 300 days of data, return
  if(context$i < 300L) {
    return()
  }

  # Calculate a short term (100 day) moving average
  # by pulling history for the asset (apple) and taking an average
  short_hist <- fly_data_history(data, context$asset, "price", bar_count = 100L, frequency = "1d")
  short_mavg <- mean(short_hist)

  # Calculate a long term (300 day) moving average
  long_hist <- fly_data_history(data, context$asset, "price", bar_count = 300L, frequency = "1d")
  long_mavg <- mean(long_hist)

  # If short > long, go 100% in apple
  if(short_mavg > long_mavg) {
    fly_order_target_percent(asset = context$asset, target = 1)
  }
  # Else if we hit the crossover, dump all of apple
  else if (short_mavg < long_mavg) {
    fly_order_target_percent(asset = context$asset, target = 0)
  }

  # Record today's data
  # We record the current apple price, along with the value of the short and long
  # term moving average
  fly_record(
    AAPL = fly_data_current(data, context$asset, "price"),
    short_mavg = short_mavg,
    long_mavg = long_mavg
  )

}
```

Run the algo over a certain time period.

```{r}
performance <- fly_run_algorithm(
  initialize  = fly_initialize,
  handle_data = fly_handle_data,
  start       = as.Date("2013-01-01"),
  end         = as.Date("2016-01-01")
)

tail(performance)
```

From the `performance` tibble, we can look at the recorded value of Apple's stock price.

```{r}
library(ggplot2)
library(dplyr)
library(lubridate)

performance <- performance %>%
  mutate(date = as.POSIXct(date, "UTC"))

performance %>%
  filter(date >= "2014-08-01") %>%
  ggplot(aes(x = date, y = AAPL)) +
  geom_line()
```

We can also look at the value of our portfolio over time.

```{r}
first_order <- performance %>%
  filter(row_number() == 300) %>%
  pull(date)

performance %>%
  mutate(date = as.POSIXct(date, "UTC")) %>%
  ggplot(aes(x = date, y = portfolio_value)) +
  geom_line() +
  geom_vline(xintercept = first_order, color = "red") +
  annotate("text", x = first_order - days(50), y = 10500, 
           label = "First Order", color = "red")
```
